\section{Linkar og lesefni:}
\begin{itemize}
    \item G. Li, Z. Song, and Q. Fu, “A New Method of Image Detection for Small Datasets under
the Framework of YOLO Network”, in Proceedings of 2018 IEEE 3rd Advanced Information Technology, Electronic and Automation Control Conference, IAEAC 2018,
Institute of Electrical and Electronics Engineers Inc., Dec. 2018, pp. 1031–1035, isbn:9781538645086. doi: 10.1109/IAEAC.2018.8577214.
    \item Review of Deep Learning Methods in Robotic Grasp Detection  https://www.mdpi.com/2414-4088/2/3/57
    \item MoveIt! pathplanning  \url{https://www.researchgate.net/profile/Sachin_Chitta/publication/254057457_MoveitROS_topics/links/565a2a0608aefe619b232fa8.pdf}
    \item An Industrial Robotics Application with Cloud Computing and High-Speed Networking \url{https://ieeexplore.ieee.org/abstract/document/7926513}
    \item Automation of pot-shell maintenance using vision guided robots, Eymar Friðgeir, \url{https://skemman.is/handle/1946/34923}
\end{itemize}

\section{Bin picking}
\begin{itemize}
    \item Bin-picking \url{https://books.google.is/books?hl=en&lr=&id=BfYUCwAAQBAJ&oi=fnd&pg=PR8&dq=overview+bin+picking+&ots=HJ47793Cvp&sig=kS_8e-0EzSwMpLQrt7FYATJdz2s&redir_esc=y#v=onepage&q=overview%20bin%20picking&f=false}
    \item Automated bin picking \url{https://www.therobotreport.com/fully-automated-bin-picking-finally-here/}
    \item Robotic Bin Picking – The Holy Grail in Sight \url{https://www.robotics.org/content-detail.cfm/Industrial-Robotics-Industry-Insights/Robotic-Bin-Picking-The-Holy-Grail-in-Sight/content_id/6002}
    \item RobotWorx - The Future of Automated Random Bin Picking. [Online]. Available: \url{https://www.robots.com/blogs/the-future-of-automated-random-binpicking} (visited on 01/01/2021).
\end{itemize}

\subsection{Computer Vision}
\begin{itemize}
    \item Linkar
    \item You Ever Wanted To Know About Computer Vision. | by Ilĳa Mihajlovic |
Towards Data Science. [Online]. Available: \url{https://towardsdatascience.com/everything-you-ever-wanted-to-know-about-computer-vision-heresa-look-why-it-s-so-awesome-e8a58dfb641e} (visited on 01/03/2021).
    \item Computer vision: a modern approach \url{http://thuvienso.vanlanguni.edu.vn/handle/Vanlang_TV/17581}
    \item Computer vision: algorithms and applications \url{https://books.google.com/books?hl=en&lr=&id=bXzAlkODwa8C&oi=fnd&pg=PR4&dq=computer+vision&ots=g-Y581pDIC&sig=hiGflaAjdJQghxsmyHAp6aJgRWY}
\end{itemize}

\subsection{Neural Networks}
\begin{itemize}
    \item  A Comprehensive Guide to Convolutional Neural Networks — the ELI5 way | by Sumit
Saha | Towards Data Science. [Online]. Available: \url{https://towardsdatascience.com/a-comprehensive-guide-to-convolutional-neural-networks-theeli5-way-3bd2b1164a53} (visited on 01/09/2021).
\end{itemize}
\subsection{Incremental Learning}
rgfg

\section{Coco annotator}
\begin{itemize}
    \item jsbroks/coco-annotator: :pencil2: Web-based image segmentation tool for object detection, localization and keypoints. [Online]. Available:\url{https://github.com/jsbroks/coco-annotator}
\end{itemize}

\section{YOLO}
\begin{itemize}
    \item 
    \item J. Redmon and A. Farhadi, “YOLOv3: An Incremental Improvement”, Apr. 2018.[Online]. Available: \url{http://arxiv.org/abs/1804.02767}.
\end{itemize}


\subsection{Robot Operating System (ROS)}
\begin{itemize}
    \item M. Quigley, K. Conley, B. P. Gerkey, J. Faust, T. Foote, J. Leibs, R. Wheeler, and
A. Y. Ng, “Ros: An open-source robot operating system”, in ICRA Workshop on Open
Source Software, 2009
    \item O. S. R. Foundation, Ros.org | is ros for me?, \url{https://www.ros.org/is-rosfor-me/}, (Accessed on 01-02-2019).
    \item Ros index, \url{https://index.ros.org/packages/}, (Accessed on 01-06-2019).
\end{itemize}

% \subsection{Darknet, Ultralytics or Lightnet}
% \begin{itemize}
%     \item Understanding darknet’s yolo.cfg config files - Stack Overflow. [Online]. Available:
% \url{https://stackoverflow.com/questions/50390836/understanding-darknets-yolo-cfg-config-files} (visited on 01/10/2021).
%     \item J. Redmon, Darknet: Open source neural networks in c, 2013. [Online]. Available:
% \url{https://pjreddie.com/darknet/} (visited on 12/13/2020).
%     \item ultralytics/yolov3 at archive. [Online]. Available: \url{https://github.com/ultralyt
% ics/yolov3/tree/archive} (visited on 01/10/2021).
%     \item Lightnet documentation — Lightnet 1.1.1 documentation. [Online]. Available: \url{
%     https://eavise.gitlab.io/lightnet/} (visited on 01/10/2021).
% \end{itemize}

% \subsection{Linux operating system}
% \begin{itemize}
%     \item Ubuntu release cycle | Ubuntu. [Online]. Available: \url{https://ubuntu.com/about/release-cycle}
% \end{itemize}

% \subsection{Python}
% \begin{itemize}
%     \item What is Python? Executive Summary | Python.org. [Online]. Available: \url{https://www.python.org/doc/essays/blurb/} (visited on 01/10/2021).
% \end{itemize}

% \subsection{C}
% \begin{itemize}
%     \item C (programming language) - encyclopedia article - Citizendium. [Online]. Available:
% \url{https://en.citizendium.org/wiki/C_(programming_language)} (visited on
% 12/09/2020).

% \end{itemize}
\pagebreak

%  Ma eyða seinna\begin{itemize}
%     \item \url{https://www.intelrealsense.com/lidar-camera-l515/}
% \end{itemize}
% Má eyða seinna \begin{itemize}
%     \item \url{https://www.intelrealsense.com/lidar-camera-l515/}
% \end{itemize}
%\lipsum[14-20]
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "DEGREE-NAME-YEAR"
%%% End: 
